\papertitle

### 2021-03-04 source_separation/paper/paper.tex
Added TDCNN++ description

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcnn} (TDCNN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.\\

@@

			\subsubsection{TDCNN++}
			@Leo/Alejandro

>>>>

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcnn} (TDCNN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.\\

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCNN++, was improved by \cite{tdcnnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcnn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connections ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.\\

			TDCNN++ presents the interesting property of having almost the same architecture as TDCNN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data type used for training.
